Introduction to Moltres: an Application for Simulation of Molten Salt Reactors

### 2017-08-01 Moltres.tex
getting rid of extraneous adverbs

This work introduces Moltres, a new physics application for modeling coupled 
physics in fluid-fuelled, molten salt reactors. The neutronics model, thermal
hydraulics model, and their coupling in the MOOSE framework are
described. Neutron and precursor equations are implemented using an Action
system that allows use of an arbitrary number of groups with no change in the
input card. Results for many-channel configurations in 2D-axisymmetric and 3D
coordinates are presented and compared against other coupled models as
well as the Molten Salt Reactor Experiment.

@@

Moltres is an open source code licensed under \gls{LGPL} terms that aims to be a
tool that can be freely used, studied, interrogated, and improved by the
\gls{MSR} community.  Its openness is a defining characteristic and promotes
quality through transparency and ease of peer review. In the era of
GitHub\cite{noauthor_build_nodate} and international scientific collaboration,
open and modern software practices must be employed in order for nuclear
engineering simulation capability to enable discovery and support the regulatory
needs presented by new reactor designs. In that vein, Moltres uses
\mintinline{latex}{git} for version control, integration testing to protect
developed physics capabilities, and a C++ object-oriented design to
enable extension and code reuse. Moreover, Moltres is built on
top of the \gls{MOOSE} framework, \cite{gaston_physics-based_2015} another
\gls{LGPL} code that itself leans on LibMesh \cite{kirk_libmesh:_2006}, a
\gls{LGPL} finite element library, and PetSc \cite{satish_balay_petsc_2015}, a
\gls{BSD}-licensed toolkit for solving nonlinear equations yielded by 
discretizing PDEs. \gls{MOOSE} and LibMesh translate weak PDE forms defined by
applications (e.g. Moltres) into residual and Jacobian
functions. These functions are the inputs into PetSc Newton-Raphson solution routines. All
codes use MPI for parallel communication and are easily deployed on
massively-parallel cluster-computing platforms. \gls{MOOSE} applications by
default use monolithic and implicit methods that are ideal for closely-coupled
and multi-scale physics. These methods are ideal for the model problem described
in this work. However, it should be noted that Moltres can also use explicit
time-stepping routines as well as segregated solution methods, making it very
extensible to myriad future modeling challenges.

@@

As described earlier, Moltres runs naturally in parallel. To test its
performance, a scaling study was conducted using a typical 2D axisymmetric input
file. Moltres's performance is shown in \cref{fig:scaling_study}. The solution
time follows very closely to the ideal; slight deviations are expected due to
the expense of communication and the nature of iterative solvers. More
parallelism means more ``older'' information is used in the solution process,
which leads to slower convergence in terms of iterations \cite{satish_balay_petsc_2015}.

>>>>

Moltres is a new physics application for modeling coupled physics in 
fluid-fuelled, molten salt reactors. This paper describes its neutronics model, 
thermal hydraulics model, and their coupling in the MOOSE framework. Neutron 
and precursor equations are implemented using an Action system that allows use 
of an arbitrary number of groups with no change in the input card. Results for 
many-channel configurations in 2D-axisymmetric and 3D coordinates are presented 
and compared against other coupled models as well as the Molten Salt Reactor 
Experiment.

@@

Moltres is an open source code licensed under \gls{LGPL} terms that aims to be a
tool that can be freely used, studied, interrogated, and improved by the
\gls{MSR} community.  Its openness is a defining characteristic and promotes
quality through transparency and ease of peer review. In the era of
GitHub\cite{noauthor_build_nodate} and international scientific collaboration,
open and modern software practices must be employed in order for nuclear
engineering simulation capability to enable discovery and support the regulatory
needs presented by new reactor designs. In that vein, Moltres uses
\mintinline{latex}{git} for version control, integration testing to protect
developed physics capabilities, and a C++ object-oriented design to
enable extension and code reuse. Moreover, Moltres is built on
top of the \gls{MOOSE} framework, \cite{gaston_physics-based_2015} another
\gls{LGPL} code that itself leans on LibMesh \cite{kirk_libmesh:_2006}, a
\gls{LGPL} finite element library, and PetSc \cite{satish_balay_petsc_2015}, a
\gls{BSD}-licensed toolkit for solving nonlinear equations yielded by 
discretizing PDEs. \gls{MOOSE} and LibMesh translate weak PDE forms defined by
applications (e.g. Moltres) into residual and Jacobian
functions. These functions are the inputs into PetSc Newton-Raphson solution routines. All
codes use MPI for parallel communication and are easily deployed on
massively-parallel cluster-computing platforms. \gls{MOOSE} applications by
default use monolithic and implicit methods that are ideal for closely-coupled
and multi-scale physics. These methods are ideal for the model problem described
in this work. However, it should be noted that Moltres can also use explicit
time-stepping routines as well as segregated solution methods, making it 
extensible to myriad future modeling challenges.

@@

As described earlier, Moltres runs naturally in parallel. To test its
performance, a scaling study was conducted using a typical 2D axisymmetric input
file. Moltres's performance is shown in \cref{fig:scaling_study}. The solution
time follows closely to the ideal; slight deviations are expected due to
the expense of communication and the nature of iterative solvers. More
parallelism means more ``older'' information is used in the solution process,
which leads to slower convergence in terms of iterations \cite{satish_balay_petsc_2015}.
